Dynamic Anomaly Detection for Collective Data Via Statistical Distance

### 2017-09-28 Paper/DataAnomaly/paper.tex
Using template for paper

\usepackage[backend=bibtex]{biblatex}
\addbibresource{paper}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}

\title{Locating Data Flow Anomaly With Statistical Distance}
\author{Ruoyu Wang}
\date{2017.05.04}

@@

	\begin{abstract}
		[abstract]
	\end{abstract}

	\section{Introduction}
		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability. Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics} and the growing speed is doubling every two years.
		%In Facebook, there is about 100 terabytes of data uploaded every day~\cite{bigDataFacebook}.
		Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.

		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.
		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.
		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years. And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}. System configuration problems, as a matter of fact, also draw scratches in the messy picture. They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

@@

		On the other hand, data manipulation~\autocite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability. \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''. Taken Apache Hadoop as an example. It's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}. As is shown in Figure~\ref{fig:hadoop-security}, the two basic vulnerabilities: \textit{lack of access control} and the \textit{absence of encryption} expose the entire cluster to dangerous threats. Data flows can be intercepted and modified; services can also be altered and blocked~\autocite{huang2014denial}. Although there are several frameworks(e.g. Kerberos, Sentry, Knox etc.) and algorithms providing basic protection~\autocite{zheng2017towards,sikdar2017spatio,xu2016high,yu2015enhancing,cohen2014towards}, clever attackers can always bypass the barriers and sneak into the core of data pipelines. Several approaches are developed as sentinels to detect probable infiltrations. However, these approaches are not able to locate corrupted data under carefully planned manipulations. Nor can they figure out the exact reasons and recover the original records. To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still on demand by industry and academia.

		\begin{figure}[!t]
			\includegraphics[width=\linewidth]{fig/HadoopSecurity}
			\caption{Security Issues of Hadoop Clusters}
			\label{fig:hadoop-security}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
			\caption{Example Cumulative Distribution Function of Original And Modified Data}
			\label{fig:example-ecdf}
		\end{figure}

		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution. For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales. Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day. The curve for cheated data is emulated according to a popular method for click farming. It can be observed that there exists clearly a gap between these two distributions. 		
		%For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original. The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
		These anomalies inside data \textbf{sets/collections} will severely affect mining and learning algorithms and further change the final decision given by the entire system.

		In order to address issues caused by data manipulation, we propose a technique to detect corrupted data collections via statistical distance. As far as we know, this algorithm is the first attempt against collective data anomaly via statistical distance. Evaluations are performed on real-world and synthetic data sets, demonstrating the correctness and effectiveness of the technique.

@@

			Prevalent anomalies can be classified into \textit{Point Anomalies}, \textit{Contextual(or Conditional) Anomalies} and \textit{Collective Anomalies}. Point anomalies refers to an individual data instance that is considered anomalous with respect to others. But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly. If a group of related data(e.g. a segment of sequence) instances is anomalous with respect to other groups in the data set(e.g. the entire sequence), it is called a collective anomaly.

			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection. As the name suggests, supervised detection methods train models on completely labeled data while unsupervised detection leverages data without any labeling. Semi-supervised detection approaches train model on data that has labeled instances for only the normal class. Supervised detection is commonly applied when both normal and anomalous data can be obtained. When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.

@@

			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of buyer accounts to create fake transaction records and give high remarks on products. Professional click farmers are usually well organized groups or companies containing thousands of people. Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. Some companies even develop professional applications that can be deployed on common PCs to improve productivity\textbf{[A Citation in Chinese]}.

			A research performed in China showed that 81.9\% of the people investigated had heard of the behaviour of click farming, 51.2\% of them had seen people around them click farmed and 18.9\% of them had experience of click farming themselves\textbf{[Chinese Citation?]}. American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}.

@@

			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect. For normal sellers, their customers are usually similar since choices of products are seldom changed. Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable. No matter how much alike between the employed users or robots with honest users, the fake transaction records will always cause a bias or distortion of the original transaction distribution. Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions. This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem. Then a concrete point anomaly detection classifier can be used to find out the cheaters.

		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $S$ be a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers: 
		\begin{equation}
			D(\cdot || \cdot): S \times S \rightarrow \mathbb{R^+}
		\end{equation}

@@

		There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences. Some of them provides better properties which brings conveniences to the design and implementation of our approach.

@@

		Jensen-Shannon divergence has some fine properties:
		\begin{enumerate}
			\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in S$.
			\item $0 \le JSD_{\pi_1, \dots, \pi_n}(P_1, \dots, P_n) \le log_k(n)$. If a $k$ based algorithm is adopted.
			\item To calculate $JSD(P||Q)$, it need not necessarily to be true that $Q(i)=0$ implies $P(i)=0$.
		\end{enumerate}

	\section{Statistical Detection}\label{sec:algorithm-details}
		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records in a collection of data. For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data(e.g. Fig~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm. Main idea of the solution is simple. But there are several detailed difficulties to be solved in the design and implementation of the technique:

@@

		\subsection{Divergence-Based Collective Anomaly Detection}
			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph that each node denotes one certain collection and each edge refers to the divergence of two data collections. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous ones do not compose a large proportion of all points. However the procedure will be too complicated to work out with large amounts of instances.

			Otherwise we need a frame of reference and yielding absolute distances rather than the relative ones. Therefore, we should keep an evidence set $E$ which consists of several already known correct distributions. Then the real distribution can be estimated by averaging all distributions in $E$. This process is similar to the parameter estimation within a certain sample set. Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $E$, yielding absolute distances.

			Fig.~\ref{fig:raw-hist-1st} and~\ref{fig:raw-hist-2nd} in section~\ref{sec:exp-raw} show the result of the above process. Red dots refer to the distances calculated from normal transaction data collections, blue and green ones are from click farmed collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones are distributed around a larger distance value. Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points. The basic framework of the algorithm is shown as follows:

			\begin{algorithm}[!ht]
				\caption{Basic Classification}
				\label{alg:static}
				\begin{algorithmic}[1]
					\Require Evidence set $E = \{D_1, \dots, D_n\}(n\ge2)$; New data collection $D'$
					\Ensure Whether $D'$ is anomalous
					\For{$i \gets 1$ to $n$ do}
					\State $P_i \gets$ the distribution of $D_i$
					\EndFor
					\State $M \gets \frac{1}{n}\sum_{i=1}^{n}P_i$\label{line:population-estimation}
					\For{$i \gets 1$ to $n$ do}
					\State $J_i \gets JSD(P_i||M)$
					\EndFor
					\State $N \gets$ normal distribution estimated from $J_1, \dots, J_n$
					\State $P' \gets$ distribution of $D'$
					\State $J' \gets JSD(P'||M)$
					\State $p \gets$ probability density of $J'$ in $N$
					\If{$p <$ threshold $T$}
					\State \textbf{Return} True
					\Else
					\State \textbf{Return} False
					\EndIf
				\end{algorithmic}
			\end{algorithm}

			Let $S$ be set of the daily transaction collections, if $E$ is already given, we can run the algorithm with $E$ and $\forall D \in S$ and discover the anomalies. Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$. It is not viable for classification. Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes very large.

			According to the property of statistical divergence, we can infer that the true distribution of JSDs calculated form normal data collections are close to but not exactly a gaussian distribution $N(\mu, \sigma)$ since for each point, there are both definite upper and lower bounds instead of infinities. Therefore, $\mu$ should be slightly larger than zero. The reason why $\mu$ can not be exactly zero is hidden in line~\ref{line:population-estimation}. $M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities. Thus for a large $|S|$, $M$ may highly probably contains entries that does not exist in $P_i$ and certain probability entries in $M$ may vary from that in $P_i$. For a concrete example, suppose $P_1(1)=0.5, P_1(2)=0.3, P_1(3)=0.2$; $P_2(1) = 0.3, P_2(2) = 0.4, P_2(3) = 0.3$; $P_3(1)=0.3, P_3(3)=0.5, P_3(4)=0.2$, then $M(1) = \frac{11}{3}, M(2)=\frac{7}{3}, M(3)=\frac{10}{3}, M(4)=\frac{2}{3}$. None of $P_1, P_2, P_3$ is the same with $M$.

@@

			will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g. for normal distribution, $c=1.05$).

@@

			A naive but prevalent approach is to set a fixed value as threshold. This approach is easy to implement and may give satisfying results in specific cases. However, a fixed threshold requires analysis of the specific problem, manual observation and tuning of parameters, which involves lots of human labor. The rule of ``$3 \sigma$'' can be used to automatically determine a threshold. But in some cases that the anomalous data intersecting at the boundary with normal instances, the threshold may fail more often to discover those manipulated ones.

			However, applying divergence as the distance metric among data collection distributions provides a fine property. That is, divergences of normal data collections assemble together, forming a quasi-normal distribution. And those of anomalous data collections lies in the right-hand-side interval on the real number axis. As a result of further observation, the divergence of anomalous data collections also assemble to be a quasi-normal distribution, since statistical distance has been restricted by a strict upper bound.

			\textbf{[Better give a point drawing for each JSD value]}

			\begin{figure}[!ht]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
				\caption{Threshold Example}
				\label{fig:example-threshold}
			\end{figure}

>>>>

\usepackage[backend=bibtex]{biblatex}
\addbibresource{paper}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{color}
\title{Dynamic Anomaly Detection for Collective Data Via Statistical Distance}
%
\author{%
	% author names are typeset in 11pt, which is the default size in the author block
	{Ruoyu Wang{\small $~^{\#1}$}, Daniel Sun{\small $~^{*2}$}, Guoqiang Li{\small $~^{\#3}$} }%
	% add some space between author names and affils
	\vspace{1.6mm}\\
	\fontsize{10}{10}\selectfont\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separate superscript on following line from affiliation using narrow space
	$^{\#}$\,School of Software Engineering, Shanghai Jiao Tong University\\
	No.800 Dongchuan Rd. Shanghai, 200240, China\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	%
	% 20080211 CAUSAL PRODUCTIONS
	% in the following email addresses, separate the superscript from the email address 
	% using a narrow space \,
	% the reason is that Acrobat Reader has an option to auto-detect urls and email
	% addresses, and make them 'hot'.  Without a narrow space, the superscript is included
	% in the email address and corrupts it.
	% Also, removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{1}$\,solftwarewry@sjtu.edu.cn\\
	$^{3}$\,li.g@sjtu.edu.cn%
	% add some space between email and affil
	\vspace{1.2mm}\\
	\fontsize{10}{10}\selectfont\rmfamily\itshape
	% 20080211 CAUSAL PRODUCTIONS
	% separated superscript on following line from affiliation using narrow space \,
	$^{*}$\,Data61, Commonwealth Scientific and Industrial Research Organization, Australia\\
	\fontsize{9}{9}\selectfont\ttfamily\upshape
	% 20080211 CAUSAL PRODUCTIONS
	% removed ~ from pre-superscript since it does not seem to serve any purpose
	$^{2}$\,daniel.sun@data61.csiro.au
}

@@

	\begin{abstract}
		Hackers can infiltrate networks and find their way into databases and software systems. Not only
		can they steal chunks of data and hold them for ransom, but
		also alter key information contained in those systems, setting up
		traps hard to discover and causing damages unlikely to recover.
		Although altering single record may not oblige correct value scope such that it is hard to detect, the change, especially to a subset of data, can be observed and detected in a collective
		scale. In this paper, we present a collective anomaly
		detection technique based on statistical distance. The technique
		extracts distribution similarities among data collections, and then uses the statistical distance to detect
		collective anomalies. In order to adapt to data dynamics, our technique continuously evaluates 
		metrics as evolving features. Aiming at broad generalisation, this
		technique can replace several components of our solution to further improve the
		performance of detection for various scenarios. To illustrate details of the technique
		and explore its efficiency, we case-studied a real
		world problem of click farming detection against malicious online
		sellers. The evaluation shows that the technique maps normal
		and anomalous data collections into two distinct clusters by yielding
		efficient classifiers. Those classifiers are sensitive sufficiently to
		a much smaller magnitude of data alerting, compared with real
		world malicious behaviours--that is--it is applicable in the real world.

		%Hackers can infiltrate networks via any attack vector, find their way into databases and applications. Not only can they steal chunks of data and hold them for ransom, but also alter key information contained in those systems, setting up traps hard to discover and causing damages unlikely to recover. Although the influence of data altering is not significant in single data record, the change can be observed and detect in a collective scale.
		%In this paper, we present a dynamic collective anomaly detection technique based on statistical distance. The technique extracts distribution similarities among data collections, reducing collective anomalies into point anomalies. It dynamically calculate metrics which is adaptive to the slightly evolving features. This technique provides a basic solution where several components can be replaced by other scenario specific ones, further improving the performance of detection.
		%To illustrate details of the technique and explore its efficiency, we applied the algorithm into a real world problem of click farming detection against malicious online sellers. The evaluation shows that the technique maps normal and anomalous data collections into two distinct clusters, yielding efficient classifiers. And those classifiers are sensitive enough to a much smaller magnitude of manipulation compared with real world malicious behaviours.
	\end{abstract}

	\section{Introduction}
		Major improvements in data acquisition, transmission and storage are driving increased data availability and affordability. Currently, there are totally 2.7ZB data in the digital universe~\autocite{bigDataStatistics} and the growing speed is doubling every two years.
		%In Facebook, there is about 100 terabytes of data uploaded every day~\cite{bigDataFacebook}.
		%Big data analysis has been widely adopted in scientific experiments~\autocite{nothaft2015rethinking}, electric business~\autocite{bronson2015open,sumbaly2013big,chen2016realtime}, healthcare~\autocite{groves2016big}, governments~\autocite{kim2014big} and many other fields.
		%
		It has already been and will be much harder in the future to harness the exploding volumes of data which is now pervasive leading to many problems in data management and engineering, threatening trustworthiness and reliability of data flows inside working systems.

		Data error rate in enterprises is approximately 1\% to 5\%, and for some, even above 30\%~\autocite{saha2014data}.
		In 2016, according to the research by Tricentis~\cite{softwareFailure}, software failures cost \$1.1 trillion US dollars in total and those at 363 investigated companies affected 4.4 billion customers, causing the total lost time of more than 315.5 years. And it takes more than 45\% of total expense to eliminate those errors~\cite{pawar2016software}. System configuration problems, as a matter of fact, also draw scratches to the messy picture. They take even dominant places in failures in large distributed clusters~\cite{xu2015systems}.

@@

		On the other hand, data manipulation~\autocite{dataManipulation} from outside hackers composes another potential threat of data quality and reliability. \textit{Data Manipulation} here, according to a NSA definition, refers to that ``hackers can infiltrate networks via any attack vector, find their way into databases and applications and change information contained in those systems, rather than stealing data and holding it for ransom''.
		% Take an example of Apache Hadoop, Hadoop's security issues has long been discussed within communities and industry~\autocite{sharif2015current,terzi2015survey,jam2014survey,sharma2014securing}. As is shown in Figure~\ref{fig:hadoop-security}, the two basic vulnerabilities: \textit{lack of access control} and the \textit{absence of encryption} expose the entire cluster to dangerous threats. Data flows can be intercepted and modified; services can also be altered and blocked~\autocite{huang2014denial}. Although there are several frameworks(e.g. Kerberos, Sentry, Knox etc.) and algorithms providing basic protection~\autocite{zheng2017towards,sikdar2017spatio,xu2016high,yu2015enhancing,cohen2014towards}, clever attackers can always bypass the barriers and sneak into the core of data pipelines. Several approaches are developed as sentinels to detect probable infiltrations. However, these approaches are not able to detect corrupted data under carefully planned manipulations. Nor can they figure out the exact reasons and recover the original records. 
		If data inside the system is compromised, they will severely affect mining and learning algorithms and further change the final decision given by the entire system. In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.
		% To locate and diagnose anomalies in data pipelines under carefully planned and disguised data manipulations are still in demand by industry and academia.

		%\begin{figure}[!t]
		%	\includegraphics[width=\linewidth]{fig/HadoopSecurity}
		%	\caption{Security Issues of Hadoop Clusters}
		%	\label{fig:hadoop-security}
		%\end{figure}

		However, from the aspect of data itself, we can still detect malicious data manipulation behaviours.
		According to our observation, typical data manipulations on numerical data will lead to a drift or distortion of its original distribution. With the reshaping measurable, we can enclose data collections with similar distribution forms inside the same cluster and filter out those strange shaped ones. In this paper, we adopt Jensen-Shannon divergence as the similarity measurement among different distributions. Comparing with a estimated ground truth, each data collection can be mapped to a single real number within a definite interval. Then a gaussian classifier can be applied to detect outliers derived from manipulated data. To automatically calculate adaptive threshold for the classifier, we keep two evidence sets for both normal points and anomalies, taking advantage of the property provided by Jensen-Shannon divergence. And those evidence sets are set to be slide windows to keep up to the evolving features in dynamic scenarios.
		%For example, a Taobao online seller's transaction records(see section~\ref{sec:exp-methodology}) can be ``click farmed'' to increase the volume of sales. Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day. The curve for cheated data is emulated according to a popular method for click farming. It can be observed that there exists clearly a gap between these two distributions. 		
		%For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original. The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
		Details of the technique are put together with a real world problem of ``Click Farming'' and had been evaluated on both raw and synthetic data sets corresponding to the problem, demonstrating the correctness and effectiveness of the technique.

@@

			Prevalent anomalies can be classified into \textit{Point Anomalies}, \textit{Contextual(or Conditional) Anomalies} and \textit{Collective Anomalies}. Point anomalies refers to an individual data instance that is considered anomalous with respect to others. But if it is anomalous only in certain circumstances or a specific context, the instance is regarded as contextual anomaly. If a group of related data(e.g. a segment of sequence) instances is anomalous with respect to other groups in the data set(e.g. the entire sequence), it is called a collective anomaly~\cite{goldberger2000components}.

			Detection approaches can be categorized into three types according to whether data is labeled: \textit{Supervised}, \textit{Semi-Supervised} and \textit{Unsupervised} anomaly detection. As the name suggests, supervised detection methods train models on completely labeled data while unsupervised detection leverages data without any labeling. Semi-supervised detection approaches train model on data that has labeled instances for only the normal class. Supervised detection is commonly applied when both normal and anomalous data can be obtained.~\cite{fujimaki2005approach} When it comes to the circumstances that anomalous data is hard to obtain or there exist too many diverse types of anomalies to enumerate, semi-supervised or unsupervised approaches are usually taken into consideration.

@@

			The most popular approach to manipulate transaction and reputation data is \textit{Click Farming}, where sellers use a large number of buyer accounts to create fake transaction records and give high remarks on products. Professional click farmers are usually well organized groups or companies containing thousands of people. Leaders of such groups receive orders from sellers and assign tasks to other members to create fake transactions. Some companies even develop professional applications that can be deployed on common PCs to improve productivity~\cite{zhao2016on}.

			A research performed in China showed that 81.9\% of the people investigated had heard of the behaviour of click farming, 51.2\% of them had seen people around them click farmed and 18.9\% of them had experience of click farming themselves~\cite{yan2015report}. American researchers reported in 2015 that over 11000 sellers were detected to have click farmed records and only 2.2\% of 4000 investigaed sellers had been penalized because of the cheating attempts~\cite{netease2015research}.

@@

			Although it is hard to classify users as honest and malicious, we can still find clues from the sellers' aspect. For normal sellers, their customers are usually similar since choices of products are seldom changed. Therefore, the distribution of transactions in a fixed period of time, say one day, is relatively stable. No matter how much alike between the employed users or robots with honest users, the fake transaction records will always cause a bias or distortion of the original transaction distribution. To better observe the problem, we downloaded a real world data set containing Taobao online sellers' transaction records(see section~\ref{sec:exp-methodology}) and emulated the circumstances if it had been click farmed. Figure~\ref{fig:example-ecdf} shows the difference between one daily distribution with and without click farming.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
				\caption{Example Cumulative Distribution Function of Original And Click Farmed Daily Transaction Data}
				\label{fig:example-ecdf}
			\end{figure}

			Thus, if we can measure the similarity between different transaction distributions, there is still a chance for us to detect dishonest sellers.

	\section{Preliminaries}\label{sec:preliminaries}
		Statistical divergence, also called statistical distance, measures the similarity between two or more distributions.
		% This mathematical tool can be adopted in our solution to map distributions into one dimensional points, turning collective anomaly detection problem into point anomaly detection problem. Then a concrete point anomaly detection classifier can be used to find out the cheaters.
		Mathematically, statistical divergence is a function which describes the ``distance'' of one probability distribution to the other on a statistical manifold. Let $S$ be a space of probability distributions, then a divergence is a function from $S$ to non-negative real numbers: 
		\begin{equation}
			D(\cdot || \cdot): \mathbb{S} \times \mathbb{S} \rightarrow \mathbb{R^+}
		\end{equation}

@@

		For our purposes, we do not require the function $D$ to have the property: $D(P||Q) = D(Q||P)$. But we do need it to be true that if $Q$ is more similar with $P$ than $U$, then $D(Q||P) < D(U||P)$. There are many ways to calculate divergence, such as f-divergences, M-divergences and S-divergences.
		%Some of them provides better properties which brings conveniences to the design and implementation of our approach. 
		Considering that the sensitivity and computational cost of the function are directly related to the performance of our technique, we chose Jensen-Shannon divergence which is derived from Kullback-Leibler as the measurement.

@@

		Jensen-Shannon divergence has some fine properties:
		\begin{enumerate}
			\item $JSD(P||Q) = JSD(Q||P), \forall P, Q\in \mathbb{S}$.
			\item $0 \le JSD_{\pi_1, \dots, \pi_n}(P_1, \dots, P_n) \le log_k(n)$. If a $k$ based algorithm is adopted.
			\item To calculate $JSD(P||Q)$, it need not necessarily to be true that $Q(i)=0$ implies $P(i)=0$.
		\end{enumerate}

	\section{Statistical Detection}\label{sec:algorithm-details}
		Diverse data sets in the real world show certain structures caused by hidden patterns or relationships among records in a collection of data. For example, the traffic volume in the highway and the business transaction records, they may show a relatively stable distribution in the daily scale. Manipulation on those data(e.g. Fig~\ref{fig:example-ecdf}) results in a drift or distortion of the distribution, which can be captured to trigger the alarm. Main idea of the solution is simple. But there are several difficulties to be solved in the design and implementation of the technique:

@@

		\ref{sec:alg-basic} answers the first question and introduces a basic framework of our technique. The second question is studied in~\ref{sec:alg-histogram}. \ref{sec:alg-threshold} gives an analysis about adaptive metric that minimizes total error. And a dynamic framework is proposed in~\ref{sec:alg-dynamic}.

		\subsection{Divergence-Based Collective Anomaly Detection}\label{sec:alg-basic}
			From section~\ref{sec:preliminaries} we know that statistical divergence only provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph that each node denotes one certain collection and each edge refers to the divergence of two data collections. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous ones do not compose a large proportion of all points. However the procedure will be too complicated to work out with large amounts of instances.

			Otherwise we need a frame of reference and yielding absolute distances rather than the relative ones. Therefore, we should keep an evidence set $\mathbb{E}$ which consists of several already known correct distributions. Then the real distribution can be estimated by averaging all distributions in $\mathbb{E}$. This process is similar to the parameter estimation within a certain sample set. Let $M$ denote the estimated population distribution, then we can measure the statistical distance with respect to $M$ for every distribution $D$ inside or outside $\mathbb{E}$, yielding absolute distances.

			Fig.~\ref{fig:raw-hist-1st} and~\ref{fig:raw-hist-2nd} in section~\ref{sec:exp-raw} show the result of the above process. Red dots refer to the distances calculated from normal transaction data collections, blue and green ones are from click farmed collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones are distributed around a larger distance value. Intuitively, a simple gaussian classifier can be suitable here to discover anomalous data points. The basic framework of the algorithm is shown in Algorithm~\ref{alg:static}:

			\begin{algorithm}[!t]
				\caption{Basic Classification}
				\label{alg:static}
				\begin{algorithmic}[1]
					\Require Evidence set $\mathbb{E} = \{D_1, \dots, D_n\}(n\ge2)$; New data collection $D'$
					\Ensure Whether $D'$ is anomalous
					\For{$i \gets 1$ to $n$ do}
					\State $P_i \gets$ the distribution of $D_i$
					\EndFor
					\State $M \gets \frac{1}{n}\sum_{i=1}^{n}P_i$\label{line:population-estimation}
					\For{$i \gets 1$ to $n$ do}
					\State $J_i \gets JSD(P_i||M)$
					\EndFor
					\State $N \gets$ normal distribution estimated from $J_1, \dots, J_n$
					\State $P' \gets$ distribution of $D'$
					\State $J' \gets JSD(P'||M)$
					\State $p \gets$ probability density of $J'$ in $N$
					\If{$p <$ Threshold}
					\State \textbf{Return} True
					\Else
					\State \textbf{Return} False
					\EndIf
				\end{algorithmic}
			\end{algorithm}

			Let $\mathbb{S}$ be set of the daily transaction collections, if $\mathbb{E}$ is already given, we can run the algorithm with $\mathbb{E}$ and $\forall D \in \mathbb{S}$ and discover the anomalies. Although it is convenient to compute $JSD(P_1, \dots, P_n, P')$ instead of $JSD(P_1||M), \dots, JSD(P_n||M), JSD(P'||M)$, it is not viable for classification. Jensen-Shannon divergence of $n+1$ distributions will dilute the affection of the abnormal one, in which case the difference between $P'$ being normal and anomalous will become subtle when $n$ goes very large. For example, suppose $P(1) = P(2) = P(3) = \frac{1}{3}$ and $P'(1) = \frac{1}{6}, P'(2) = \frac{1}{3}, P'(3) = \frac{1}{2}$, then $JSD(P||P') \approx 0.023$ and $JSD(P, P, P, P') \approx 0.017$.

			According to the property of statistical divergence, we can infer that the true distribution of JSDs calculated form normal data collections are close to but not exactly a gaussian distribution $N(\mu, \sigma)$ since for each point, there are both definite upper and lower bounds instead of infinities. Therefore, $\mu$ should be slightly larger than zero. The reason why $\mu$ cannot be exactly zero is hidden in line~\ref{line:population-estimation}.
			For $\mu = 0$ if and only if $J_i = 0$ for $\forall i = 1, \dots, n$, which is equivalent to $P_i = P_j$ for $\forall i, j = 1, \dots, n$. And, $\lim_{n\rightarrow+\infty}P(P_i = P_j,\forall i, j = 1, \dots, n)=0$. Thus it is highly unlikely for real world data sets to have $u=0$.
			%$M$ takes into consideration all existing values in every distribution sample and averages corresponding probabilities. Thus for a large $|S|$, $M$ may highly probably contains entries that does not exist in $P_i$ and certain probability entries in $M$ may vary from that in $P_i$. For a concrete example, suppose $P_1(1)=0.5, P_1(2)=0.3, P_1(3)=0.2$; $P_2(1) = 0.3, P_2(2) = 0.4, P_2(3) = 0.3$; $P_3(1)=0.3, P_3(3)=0.5, P_3(4)=0.2$, then $M(1) = \frac{11}{3}, M(2)=\frac{7}{3}, M(3)=\frac{10}{3}, M(4)=\frac{2}{3}$. None of $P_1, P_2, P_3$ is the same with $M$.

@@

			will give a best partition, where $c$ is a constant relative to the shape of distribution(e.g. for normal distribution, $c=1.05$). For data sets with a large number of elements, a random sampling method, such as Monte-Carlo method, can be applied to speed up the estimation procedure.

@@

			A naive but prevalent approach is to set a fixed value as threshold. This approach is easy to implement and may give satisfying results in specific cases. However, a fixed threshold requires specific analysis in the certain scenario, manual observation and tuning of parameters, which involves lots of human labour. The rule of ``$3 \sigma$'' can be used to automatically determine a threshold. But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimal when concrete data is provided. It would be either higher than the optimum if anomalous data lies far away from the cluster consisting normal data records, or lower than the optimum if the anomalies sit more within the boundary.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/JSD-Dist.png}
				\caption{Distribution of JSD values for everyday data collection. It can be approximately regarded as a gaussian distribution.}
			\end{figure}

			However, applying divergence as the distance measurement among data collection distributions provides a fine property. That is, divergences of normal data collections assemble together, forming a quasi-gaussian distribution. And those of anomalies also form a quasi-guassian distribution which lies in the right-hand-side interval on the real number axis. As a result of further observation, however, true distribution of both JSDs derived from normal and anomalous data collections may differ a little more from the standard gaussian than the expected estimation error. That is due to the unknown randomness within real world data. Few assumptions can be applied in real world data sets, let alone data volume is sometimes relatively low. This topic is out of the domain discussed in this paper and we here only introduce the technique instead of the specific distribution model. However, in the scenarios that better models can be calculated, distributions here can be replaced to produce better results. For the simplicity of our proposal, we assume the distributions of JSDs to be gaussian.
			%the divergence of anomalous data collections also assemble to be a quasi-normal distribution, since statistical distance has been restricted by a strict upper bound.

			\textbf{[Better give a Histogram drawing JSD distribution]}

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
				\caption{Threshold can be determined either by a probability density value, or a radius from the centre. In the scenario shown in the figure, the threshold can be determined by the position between two means of the distribution, denoted as ``T'' here. This form of threshold can also be applied to other types of distributions even there is no intersection between these two.}
				\label{fig:example-threshold}
			\end{figure}
